Appendix 2 - Fitting proposed path models using the C-statistic

### 2015-04-03 report_dbh_problems.Rmd
Code to subset tagged stem DBH data and send along for use in FVS simulation. Typo correction in the report Rmd file. Minor line corrections and edits to add/change titles of some of the plots in the explore_data script.

#### Stems with a negative change in DBH > 15 cm (14)
 - For stems 4797 & 4795 I calculated an estimate for the original DBH based on a linear relationship between measurements from 2012 and 2014 because the original measurements recorded were most likelyl circumference. I initially did a simple coversion from circumference to diameter, but this resulted in values that were substantially hire than the measurements in either 2012 or 2014. New values for 2009 will be: stem 4797 = 7.8, stem 4795 = 10.0

>>>>

#### Stems with a negative change in DBH > 15 cm (14)
 - For stems 4797 & 4795 I calculated an estimate for the original DBH based on a linear relationship between measurements from 2012 and 2014 because the original measurements recorded were most likely circumference. I initially did a simple coversion from circumference to diameter, but this resulted in values that were substantially hire than the measurements in either 2012 or 2014. New values for 2009 will be: stem 4797 = 7.8, stem 4795 = 10.0
